Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2020-12-03 manuscript/manuscript.tex
Partial draft of manuscript methods

We used optimal estimation as implemented in the ``Isofit'' Python library~\cite{thompson2019optimal,thompson2018optimal}.

>>>>

\subsection{Input data}\label{subsec:input-data}

We obtained atmospherically corrected surface reflectance imaging spectroscopy data from a National Ecological Observatory (NEON) Airborne Observing Platform (AOP) scene in the Upper East River basing of Colorado, USA (39.0$^{\circ}$ N, 106.9$^{\circ}$ W) as processed by \citeA{chadwick2020integrating} and available on Google Earth Engine under the collection %\texttt{users/pgbrodrick/SFA/collections/ciacorn_priority}.
A complete description of the data and processing methods are provided in \citeA{chadwick2020integrating}.
Briefly, the scene is a mosaic from several NEON AOP flights performed in summer 2018.
NEON AOP data have a spatial resolution of XXX m and an average spectral resolution of XXX nm over the range XXX nm to XXX nm. %TODO: Fill out these values.
The atmospheric correction routine was a custom application of the Atmospheric CORrection Now (ACORN‐6LX, Imspec LLC, Glendale) software package accounting for fine-scale variation in topography and sun-sensor geometry.

We used Google Earth Engine to manually select and extract 500 vegetation pixels from this scene (Figure~\ref{fig:sitemap}).
The pixels exhibit substantial variability in brightness and spectral character:
green reflectance (550 nm) ranges from XXX to XXX;
near-infrared reflectance (1100 nm) ranges from XXX to XXX;
and hyperspectral normalized difference vegetation index (NDVI; XXX and XXX nm bands) varies from XXX to XXX (Figure~\ref{fig:input-summary}).

\begin{figure}[ht]
  \centering
  % \includegraphics[]{figures/...}
  \caption{\label{fig:sitemap} \
    True color composite of the input data location, with vegetation pixels highlighted.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  % \includegraphics[options]{figures/...}
  \caption{\label{fig:input-summary} \
    Summary of 500 input reflectance spectra selected for this study.
    Main figure shows 10 example spectra (black lines) and the full range of the input reflectance (gray shading).
    Inset figure shows a histogram of hyperspectral normalized difference vegetation index (NDVI;\@red=XXXnm, NIR=XXXnm) across the 500 input spectra.
  }
\end{figure}

\subsection{Simulation workflow}\label{subsec:workflow}

To explore the contributions of different uncertainty sources, we performed a simulation workflow that consisted of three major steps:
First, starting from known surface reflectance (Section~\ref{subsec:input-data}), we simulated radiance as it would be measured by a satellite, accounting for different combinations of surface elevation, atmospheric composition, sun-sensor geometry, and detector characteristics (e.g., signal-to-noise ratio) (Section~\ref{subsec:}).
Second, for each of these simulated measurements, we performed atmospheric correction to estimate surface reflectance with uncertainty.
Third, for each of these estimated reflectance spectra, we estimated plant traits using existing models.

\subsubsection{Simulating measured radiance}\label{subsubsec:radiance}

Following \citeA{thompson2018optimal}, we model top-of-atmosphere radiance ($L_{TOA}$) as a function of incoming solar irradiance ($e_{0}$), surface reflectance ($\rho_{s}$), and three terms describing atmospheric optical properties:
the path reflectance ($\rho_{a}$), transmittance ($t$), and spherical albedo ($s$).
Assuming that the entire reflectance process is Lambertian, and accounting for the solar zenith angle ($\theta_{s}$), the expression for TOA radiance is:

\begin{linenomath*}
\begin{equation}
  L_{TOA} = \frac{e_{0}\cos(\theta_{s})}{\pi}\left( \rho_{a} + \frac{t \rho_{s}}{1 - s \rho_{s}} \right)
\end{equation}
\end{linenomath*}

To simulate top-of-atmosphere radiance, we used a hybrid approach recently developed by Broderick et al.~\emph{in review} (sRTMnet)that combines an atmospheric radiative transfer model (RTM) based on a computationally efficient successive orders of scattering approximation~\cite<Second Simulation of a Satellite Signal in the Solar Spectrum-Vector, 6SV, version 2.1,>{kotchenova2006validation} with a neural network-based emulator of a more advanced RTM~\cite<MODTRAN,>{berk2017validation}.

For a given combination of surface elevation and atmospheric conditions (aerosol optical depth and water vapor content), we simulated

\subsubsection{Atmospheric correction via optimal estimation}\label{subsubsec:isofit}

We used optimal estimation as implemented in the ``Isofit'' Python library~\cite{thompson2019optimal,thompson2018optimal}.
As the underlying atmospheric RTM, we used the same hybrid sRTMnet approach as described in Section~\ref{subsubsec:radiance}.

\subsubsection{Estimating plant functional traits}\label{subsubsec:traits}

\subsection{Analysis}\label{subsec:analysis}

We quantified the contributions of each uncertainty source to both estimates of surface reflectance and the final trait estimates.
